NFC and burnout in teachers - A replication and extension study

### 2021-10-28 Manuscript/Manuscript.Rmd
added table for DRR model

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

  replicationyears_table <-
    kbl(fityears_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```

>>>>

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

  replicationyears_table <-
    kbl(fityears_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
```{r fit2_table, echo=FALSE, message=FALSE, warning=FALSE}

  fit2_table <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
                                      "DTH $\\rightarrow$ MBI", "DTL $\\rightarrow$ MBI", "DRF $\\rightarrow$ MBI",
                                      "NFC $\\rightarrow$ MBI via DTH", "NFC $\\rightarrow$ MBI via DTL", "NFC $\\rightarrow$ MBI via DRF",
                                      "Total Effect"),
                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

  fit2_table[2:ncol(fit2_table)] <- format(round(fit2_table[2:ncol(fit2_table)], digits = 3), nsmall = 2)

  drrmodel_table <-
    kbl(fit2_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```
